Dirac neutrino mass generation from Majorana messenger

### 2019-09-11 draft.tex
sf

The cross section is given in~\cite{Barger:2003zh}, in the case with heavy mediator $T^{\nu_R}_{\text{dec}} \ll M_{Z^{\prime}}$, we can to take the limit when $s \ll M_{Z^{\prime}}$ and neglecting the fermion masses, we have that the cross section is
%
\begin{align*}
    \sigma_{f}(s) \approx N^{C}_{f} \frac{s}{12 \pi} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} Q^{2}_{\nu_R} (Q^{2}_{f_L} + Q^{2}_{f_R})\,,
\end{align*}
%
where $N^{C}_{f}$ is the color multiplicity of the fermion, i.e. $N^{C}_{q(\ell)} = 3(1)$, $Q_{f}$ is the charge of the fermion under the new symmetry, $g^{\prime}$ and $M_{Z^{\prime}}$ are the gauge coupling and mass for the new gauge boson. Solving the integrals with this last cross section we obtain that the interaction rate is given by
%
\begin{align*}
    \Gamma_{\nu_{R}}(T) = \frac{49 \pi^{5} T^{5}}{97200 \zeta(3)} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} \sum_{f} N^{C}_{f} Q^{2}_{f}\,,
\end{align*}
%
where the sum is performed over all SM fermion that are in thermal equilibrium with the plasma at temperature $T$. To estimate the contribution to the relativistic degrees of freedom for neutrinos, it is necessary to calculate the decoupling temperature of the right neutrinos ($T^{\nu_R}_{\text{dec}}$). The latter occurs when the interaction rate of neutrinos with the SM drop below the rate of expansion of the universe, i.e.
%
\begin{align*}
\Gamma(T^{\nu_R}_{\text{dec}}) = H(T^{\nu_R}_{\text{dec}})\,, 
\end{align*}
% \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,,

where the Hubble expansion parameter is
% \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,,

\begin{align*}
    H(T) = \sqrt{\frac{8 \pi G_{N} \rho(T)}{3}} = \sqrt{\frac{4 \pi^{3} G_{N}}{45} \left( g(T) + \frac{21}{4} \right)} T^{2}\,,
\end{align*}
%
where $21/4$ correspond to the contribution of the right neutrinos to relativistic degrees of freedom. By finding the decoupling temperature of the right neutrinos $T^{\nu_R}_{\text{dec}} $ by a root finding method, it is possible to calculate $\Delta N_{\text{eff}}$.

The results of $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are exhibited in fig.~\ref{fig:Neff}. We can see that for small decoupling temperatures, the variation in the number of relativistic degrees of freedom of the new species is large and vice versa. The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Alioli:2017nzr}. For our model we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$TeV in order to satisfy the conditions of $N_{eff}$ for all the symmetries studied here.

>>>>

The cross section is given in~\cite{Barger:2003zh}, in the case with heavy mediator $T^{\nu_R}_{\text{dec}} \ll M_{Z^{\prime}}$, we can to take the limit when $s \ll M_{Z^{\prime}}$ and neglecting the fermion masses, we have that the cross section is
%
\begin{align*}
    \sigma_{f}(s) \approx N^{C}_{f} \frac{s}{12 \pi} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} Q^{2}_{\nu_R} (Q^{2}_{f_L} + Q^{2}_{f_R})\,,
\end{align*}
%
where $N^{C}_{f}$ is the color multiplicity of the fermion, i.e. $N^{C}_{q(\ell)} = 3(1)$, $Q_{f}$ is the charge of the fermion under the new symmetry, $g^{\prime}$ and $M_{Z^{\prime}}$ are the gauge coupling and mass for the new gauge boson. Solving the integrals with this last cross section we obtain that the interaction rate is given by
%
\begin{align*}
    \Gamma_{\nu_{R}}(T) = \frac{49 \pi^{5} T^{5}}{97200 \zeta(3)} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} \sum_{f} N^{C}_{f} Q^{2}_{f}\,,
\end{align*}
%
where the sum is performed over all SM fermion that are in thermal equilibrium with the plasma at temperature $T$. To estimate the contribution to the relativistic degrees of freedom for neutrinos, it is necessary to calculate the decoupling temperature of the right-handed neutrinos ($T^{\nu_R}_{\text{dec}}$). The latter occurs when the interaction rate of neutrinos with the SM drop below the rate of expansion of the universe, i.e.
%
\begin{align*}
\Gamma(T^{\nu_R}_{\text{dec}}) = H(T^{\nu_R}_{\text{dec}})\,, 
\end{align*}
% \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,, 
%
where the Hubble expansion parameter is
% \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,, 
%
\begin{align*}
    H(T) = \sqrt{\frac{8 \pi G_{N} \rho(T)}{3}} = \sqrt{\frac{4 \pi^{3} G_{N}}{45} \left( g(T) + \frac{21}{4} \right)} T^{2}\,,
\end{align*}
%
where $21/4$ correspond to the contribution of the right neutrinos to relativistic degrees of freedom. By finding the decoupling temperature of the right neutrinos $T^{\nu_R}_{\text{dec}} $ by a root finding method, it is possible to calculate $\Delta N_{\text{eff}}$.

The results of $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are exhibited in fig.~\ref{fig:Neff}. We can see that for small decoupling temperatures, the variation in the number of relativistic degrees of freedom of the new species is large and vice versa. The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Alioli:2017nzr}. For our model we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$TeV in order to satisfy the conditions of $N_{\text{eff}}$ for all the symmetries studied here.
